Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-03-19 Cost_manuscript.Rmd
acknowledgments and fixed citations

This project was funded.... In addition, we would like to thank Andrew Westbrook, the Shenhav lab, and Daw lab for valuable feedback.

>>>>

We thank Andrew Westbrook, the Shenhav lab, and the Daw lab for helpful discussions. This work was supported by grants from the National Science Foundation (BCS-1755757) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
